Mergeable Types

### 2017-02-27 paper/semantics.tex
Semantics.

The function \C{lca} used in the premise of \rulelabel{E-Pull-Wait}
computes the LCA of two branches. The function is in fact a partial
function because the definition of LCA doesn't guarantee its
uniqueness for a pair of branches. Such nuances of LCA, and the
guarantees provided by the system notwithstanding these nuances, are
discussed in the subsection~\ref{sec:meta}.

>>>>

The function \C{lca} used in the premise of \rulelabel{E-Pull-Wait}
computes the LCA of two branches, and assumes it to be unique.  But,
observe that the definition of LCA doesn't guarantee its uniqueness;
it has to be enforced explicitly.  The semantics enforces the
uniqueness of LCA by constraining the branching structure via the
\rulelabel{E-Pull-Wait} rule. The rule merges version $v'$ into
version $v$ only if they are \emph{safely mergeable} (denoted
$\under{H}{v' \mbleto t}$), i.e., they have a single LCA, and merging
both versions does not lead to a case where a branch has multiple LCAs
with rest of the branches, hence gets \emph{stuck}. Such nuances of
LCA, and the guarantees provided by the system notwithstanding these
nuances, are discussed in the subsection~\ref{sec:meta}.
